Making Q-learning robust to time discretization

### 2019-01-17 paper/icml_drau/relatedworks.tex

Our approach builds on \cite{adv_upd}, who identified the collapse of
Q-learning for small time steps and, as a solution, suggested the Advantage
Updating algorithm, with proper $\deltat$ scalings for the $V$ part and
the advantage part; testing was only done on a quadratic-linear problem.
We expand on \cite{adv_upd} in several directions. First, we modify the
algorithm by
using a different normalization step for $A$, which forgoes the need to
learn the normalization itself, thanks to the parameterization
\eqref{eq:Aparam}. Second, we test Advantage Updating for the first time on a
variety on RL environments using deep networks, establishing Deep
Advantage Updating as a viable algorithm in this setting.  Third,
we provide formal proofs in a general setting for the collapse of Q-learning when $\deltat\to
0$, and for the non-collapse of Advantage Updating with the proper scalings.
Fourth, we also discuss how to obtain $\deltat$-invariant exploration. Fifth, we
provide stringent experimental tests of the actual robustness to changing
$\deltat$.
%  \cite{adv_upd} already separated the learning procedure of the
% value and advantage functions, and introduced proper scalings between the two
% components. We extend on \cite{adv_upd} in three directions. We provide a
% formal argument on why the advantage contribution of the Q-function is of order
% $\bigO(\deltat)$, irrelevant of the stochasticity of the environment, in a quite
% general framework. We show that, provided with well suited learning rates and
% exploration method, Advantage updating provide near invariance to change of time
% discretization. We show that Advantage updating is viable in the context of deep
% reinforcement learning, while not using the true gradient of the residual error.

\TODO{Say that Actor-critic has no problem when $\deltat\to 0$?}

More recently, \cite{dueling_nets} also introduced a parameterization separating
the value and the advantage components of the Q-function. Contrary to
\cite{advup}'s Advantage Updating, learning is still done in a standard
way on the $Q$-function obtained from adding these two components. Thus this
approach reparameterizes $Q$ but does not introduce the proper scalings
and does not result in an invariant algorithm for small $\deltat$.%We additionally
%introduce a natural scaling coeficient between the two, that strongly improves
%the time discretization invariance properties.

>>>>

Our approach builds on \cite{adv_upd}, who identified the collapse of
Q-learning for small time steps and, as a solution, suggested the Advantage
Updating algorithm, with proper $\deltat$ scalings for the $V$ part and
the advantage part; testing was only done on a quadratic-linear problem.

We expand on \cite{adv_upd} in several directions. First, we modify the
algorithm by
using a different normalization step for $A$, which forgoes the need to
learn the normalization itself, thanks to the parameterization
\eqref{eq:Aparam}. Second, we test Advantage Updating for the first time on a
variety on RL environments using deep networks, establishing Deep
Advantage Updating as a viable algorithm in this setting.  Third,
we provide formal proofs in a general setting for the collapse of Q-learning when $\deltat\to
0$, and for the non-collapse of Advantage Updating with the proper scalings.
Fourth, we also discuss how to obtain $\deltat$-invariant exploration. Fifth, we
provide stringent experimental tests of the actual robustness to changing
$\deltat$.
%  \cite{adv_upd} already separated the learning procedure of the
% value and advantage functions, and introduced proper scalings between the two
% components. We extend on \cite{adv_upd} in three directions. We provide a
% formal argument on why the advantage contribution of the Q-function is of order
% $\bigO(\deltat)$, irrelevant of the stochasticity of the environment, in a quite
% general framework. We show that, provided with well suited learning rates and
% exploration method, Advantage updating provide near invariance to change of time
% discretization. We show that Advantage updating is viable in the context of deep
% reinforcement learning, while not using the true gradient of the residual error.

\TODO{Say that Actor-critic has no problem when $\deltat\to 0$? With SGD
but not with RMSProp, and needs robust exploration}

More recently, \cite{dueling_nets} also introduced a parameterization separating
the value and the advantage components of the Q-function. Contrary to
\cite{adv_upd}'s Advantage Updating, learning is still done in a standard
way on the $Q$-function obtained from adding these two components. Thus this
approach reparameterizes $Q$ but does not introduce the proper scalings
and does not result in an invariant algorithm for small $\deltat$.%We additionally
%introduce a natural scaling coeficient between the two, that strongly improves
%the time discretization invariance properties.
